comgen-outline

### 2017-06-10 paper/comgen-paper.Rmd
remove print statements, etc.

  d.hab.priors.samples <- bind_rows(
    d.hab.priors.samples,
    d.hab.priors.filtered %>% 
    select(workerid, item, starts_with("annualRate"), 
           starts_with("mixture")) %>%
    rowwise() %>%
    mutate(
      stable_male = rbinom(n = 1, size = 1, prob = mixture_male),
       freq_male = ifelse(stable_male == 1, annualRate_male, 0.007),
       stable_female = rbinom(n = 1, size = 1, prob = mixture_female),
       freq_female = ifelse(stable_female == 1, annualRate_female, 0.007)
       ) %>%
    select(item, freq_male, freq_female) %>%
    gather(gender, val, freq_male, freq_female) %>%
  mutate(gender = gsub("freq_", "", gender))
  )
  print(i)
}

@@

  rs.habituals.bda.prior <- bind_rows(
    rs.habituals.bda.prior, 
    rs %>% 
      mutate(item = it) %>% 
      separate(Parameter, into = c("Variable", "Parameter", "Gender"))
  )
}

rs.habituals.bda.prior %>% 
  mutate(param = paste(Variable, Parameter, sep = "_")) %>%
  select(-Variable, -Parameter, -Chain) %>%
  spread(param, value) 
```

>>>>

  d.hab.priors.samples <- bind_rows(
    d.hab.priors.samples,
    d.hab.priors.filtered %>% 
    select(workerid, item, starts_with("annualRate"), 
           starts_with("mixture")) %>%
    rowwise() %>%
    mutate(
      stable_male = rbinom(n = 1, size = 1, prob = mixture_male),
       freq_male = ifelse(stable_male == 1, annualRate_male, 0.007),
       stable_female = rbinom(n = 1, size = 1, prob = mixture_female),
       freq_female = ifelse(stable_female == 1, annualRate_female, 0.007)
       ) %>%
    select(item, freq_male, freq_female) %>%
    gather(gender, val, freq_male, freq_female) %>%
  mutate(gender = gsub("freq_", "", gender))
  )
}

@@

  rs.habituals.bda.prior <- bind_rows(
    rs.habituals.bda.prior, 
    rs %>% 
      mutate(item = it) %>% 
      separate(Parameter, into = c("Variable", "Parameter", "Gender"))
  )
}
```
